You've got a $5 \times 5$ matrix, consisting of 24 zeroes and a single number one.
Let's index the matrix rows by numbers from 1 to 5 from top to bottom, let's
index the matrix columns by numbers from 1 to 5 from left to right. In one move,
you are allowed to apply one of the two following transformations to the
matrix:

\begin{itemize}
    \item Swap two neighboring matrix rows, that is, rows with indexes $i$ and
    $i+1$ for some integer $i $$(1 \leq i < 5)$;
    \item Swap two neighboring matrix columns, that is, columns with indexes $j$
    and $j+1$ for some integer $j $$(1 \leq j < 5)$.
\end{itemize}

You think that a matrix looks \textit{beautiful} if the single number one of the matrix
is located in its middle (in the cell that is on the intersection of the third
row and the third column). Count the minimum number of moves needed to
make the matrix beautiful.

\subsection*{Input}

The input starts with $T$, the number of test cases. Then, each test case is
given.

A test case consists of five lines, each line contains five integers: the $j-th$
integer in the $i-th$ line of the case represents the element of the matrix that
is located on the intersection of the $i-th$ row and the $j-th$ column. It is
guaranteed that the matrix consists of 24 zeroes and a single number one.

\subsection*{Output}

For each test case, print a single integer - the minimum number of moves needed to make the matrix
beautiful.

\begin{table}[!h]
\centering
\begin{tabular}{|l|l|}
\hline
\begin{minipage}[t]{3in}
\textbf{Sample Input}
\begin{verbatim}
2
0 0 0 0 0
0 0 0 0 1
0 0 0 0 0
0 0 0 0 0
0 0 0 0 0
0 0 0 0 0
0 0 0 0 0
0 1 0 0 0
0 0 0 0 0
0 0 0 0 0
\end{verbatim}
\vspace{1mm}
\end{minipage}
&

\begin{minipage}[t]{3in}
\textbf{Sample Output}
\begin{verbatim}
3
1
\end{verbatim}
\vspace{1mm}
\end{minipage} \\
\hline
\end{tabular}
\end{table}

\newpage
