\textit{Petya loves lucky numbers. Everybody knows that lucky numbers are
positive integers whose decimal representation contains only the lucky
digits 4 and 7. For example, numbers 47, 744, 4 are lucky and 5, 17, 467 are
not.}

One day Petya was delivered a string s, containing only digits. He needs to
find a string that:
\begin{itemize}
\item represents a lucky number without leading zeroes,
\item is not empty,
\item is contained in s as a substring the maximum number of times.
\end{itemize}
Among all the strings for which the three conditions given above are
fulfilled, Petya only needs the lexicographically minimum one. Find this
string for Petya.

\subsection*{Input}

The input contains several test cases. Each test case contains a single line
with a non-empty string s whose length can range from 1 to 50, inclusive.
The string only contains digits. The string can contain leading zeroes.  The
last test case is followed by a line containing a single zero. There will
not be any test case consisting of only one zero.

\subsection*{Output}

For each test case print one line with the answer to Petya’s problem. If the
sought string does not exist, print ``-1'' (without quotes).

\begin{table}[!h]
\centering
\begin{tabular}{|l|l|}
\hline
\begin{minipage}[t]{3in}
\textbf{Sample Input}
\begin{verbatim}
047
16
472747
0
\end{verbatim}
\vspace{1mm}
\end{minipage}
&

\begin{minipage}[t]{3in}
\textbf{Sample Output}
\begin{verbatim}
4
-1
7
\end{verbatim}
\vspace{1mm}
\end{minipage} \\
\hline
\end{tabular}
\end{table}

The lexicographical comparison of strings is performed by the $\leq$ operator in
the modern programming languages. String $x$ is lexicographically less than
string $y$ either if $x$ is a prefix of $y$, or exists such $i (1 \leq i \leq
        min(|x|, |y|))$, that $x_i \leq y_i$ and for any $j (1 \leq  j \leq i)
x_j = y_j$.  Here $|a|$ denotes the length of string $a$.

In the first sample three conditions are fulfilled for strings ``4'', ``7'' and
``47''. The lexicographically minimum one is ``4''.

In the second sample s has no substrings which are lucky numbers.

In the third sample the three conditions are only fulfilled for string ``7''.

\newpage
