You are a huge fan of an online programming contest called SRM (Special Round
Match). To participate in an SRM contest, you must first download an
applet called Arena, log in to the Arena by entering your username and password,
and start competing.

Recently, to avoid hackers' attacks on the Arena, SRM imposes a new rule for the
users' passwords. From now on, the first $K$ characters of each user's password
must match its last $K$ characters. In this way, if someone enters a password with
different first and last $K$ characters repeatedly, it can be considered an attack
from hackers.

However, you love your old password and do not want to change many characters
from it. You are given a string $S$ representing your old password, and
an integer $K$. Find the minimum number of characters of $S$ that must be
changed so that the substring containing the first $K$ characters is
equal to the substring containing the last $K$ characters.

\subsection*{Input}

Each test case is described by a line containing an integer $K$ and a string $S$
($1 \leq |S| \leq 50$, $1 \leq K \leq |S|$). $S$ will contain only lowercase
English letters ($a$ - $z$).

The last test case is followed by a line containing the number zero.

\subsection*{Output}

For each test case, print the minimum number of characters of $S$ that must be
changed.

\begin{table}[!h]
\centering
\begin{tabular}{|l|l|}
\hline
\begin{minipage}[t]{3in}
\textbf{Sample Input}
\begin{verbatim}
5 topcoderopen
4 puyopuyo
3 loool
5 arena
7 amavckdkz
0
\end{verbatim}
\vspace{1mm}
\end{minipage}
&

\begin{minipage}[t]{3in}
\textbf{Sample Output}
\begin{verbatim}
3
0
1
0
5
\end{verbatim}
\vspace{1mm}
\end{minipage} \\
\hline
\end{tabular}
\end{table}

\newpage
